---
title: "Analysis of the Avian Flu dataset"
author: "Casey Crary"
date: "2023-10-23"
date-format: iso
format: pdf
editor: source
---

```{r}
#| label: setup
#| include: false
library(mosaic)   
library(tidyverse)
library(AvianFlu)
```

This file provides an overview of the AvianFlu package as well as some sample analyses.

The `AvianFlu` package contains descriptions of detections of Avian Flu as recorded by the Animal and Plant Health Inspection Service in 2022-2023.
This package may be of interest to anyone considered with poultry health.

```{r}
#| label: fig-myfigure
#| fig.cap: "Histogram of HPAI Detections Over Time, Colored by WOAH Classification"
#| warning: false
#| fig.width: 6
#| fig.height: 8
Wild_Birds |>
  ggplot(aes(x = date_detected, color = woah_classification)) +
  geom_histogram() +
  labs(x = "Date of Detection", y = "Count of HPAI detections",
       color = "WOAH classification",
       title = "Count of HPAI Detections Over Time, Colored by WOAH Classification")
```

We see in @fig-myfigure that there doesn't appear to be a general trend in HPAI detections, although it does appear that there are spikes at certain points during the year.  This could perhaps be because many birds are detected by hunters, who primarily operate in the late fall, where the spike appears to occur in 2022.  Also, most detections occur in wild birds as opposed to captive ones.
